\documentclass{ximera}

\title{Common student issues with solutions}
\author{Bart Snapp}

\begin{document}
\begin{abstract}
    Suggestions for solutions to common student issues.
\end{abstract}
\maketitle

Sometimes Ximera materials look good to instructors an others, but not to some
individual students.


\paragraph{Ximera refreshes the page when submitting}
can be caused by several issues, each with a different solution:
\begin{description}
\item[Problem:] Poor internet connection
\begin{description}
    \item[Solution:] Refresh the page immediately before entering each answer.
\end{description}
\item[Problem:] Browser settings
\begin{description}
    \item[Solution:] Try using a different browser. Different students have
reported luck with different browsers, including Edge, Firefox, and Chrome.
\end{description}
\item[Problem:] Antivirus Software
\begin{description}
    \item[Solution:] Some antivirus software (such as McAfree) are now blocking
websockets, a technology Ximera relies on. Try turning off the websockets setting on the antivirus software.

\end{description}
\item[Problem:] VPN
\begin{description}
    \item[Solution:] If you are using a VPN, try turning it off before using
Ximera.
\end{description}
\end{description}



\paragraph{Difficulty accessing Ximera} is often caused by browser settings. The
easiest solution is usually to try using a different browser. Students seem to
have the best luck with Chrome, Firefox, or Safari.


\paragraph{Work not being recorded} is almost always avoided by accessing the assignment via the LMS.

\begin{warning}
    Students who use an LTI connection \textbf{must} access Ximera from a link in your Carmen course.
They should not create a Ximera account or log into Ximera. They should be
automatically logged in from Carmen. If they are asked to log in, the connection
to Carmen is broken.
\end{warning}



\paragraph{Math processing error}

This is caused by an error in the browser setting. Two things to try:

First possible solution: Clear browser cookies. Close the browser.
Open the browser and log in to the LMS. Go to the assignment.



Second possible solution:
Find one of the pages this is happening,
Put your mouse over the `math processing error'
Now, `right-click' and select `accessibility' If collapsible math is
checked, uncheck it. Reload the page.

\paragraph{Using Ximera on an iPad}

Be sure to access Ximera via the LMS using a browser such as Safari or Chrome.
If one is having trouble accessing the Math Editor, be sure you have
updated your iPad software to the latest version.
If you are having trouble with auto-capitalization in Ximera, you can:
Hit shift twice before entering an answer to get a lower case letter.
Turn off auto-capitalization on your iPad by going to Settings $\to$ General
$\to$ Keyboards and toggling off auto-capitalization.

\end{document}